\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-01-28 motivation.tex
Updated 3

Consider a machine used to test human response time and collect this
data for future research purposes. The machine switches on a green light
on a touch screen for anywhere \textit{in between} 50.3 ms to 200.3 ms,
if the user can touch this green light then she is successful and \hj{an 
integer \texttt{1} is sent to other process in order to increase an
integer counter, if unsuccessful a \texttt{0} is sent instead to
decrease the counter}. Different statistics and analyses on human
responsiveness can be based on the collected data.

>>>>

Consider a machine used to test human response time and collect this
data for future research purposes. The machine switches on a green light
on a touch screen for anywhere \textit{in between} 50.3 ms to 200.3 ms,
if the user can touch this green light then she is successful and \hj{an
	integer \texttt{1} is sent to another process in order to increase an
	integer counter, if unsuccessful a \texttt{0} is sent instead to
decrease the counter}. Different statistics and analyses on human
responsiveness can be based on the collected data.
